\LaTeX\ Author Guidelines for ICCV Proceedings

### 2019-06-25 chapters/5_experiments_cityscapes.tex
Delete comments

% !TEX root = ../agglo_clust_review.tex
\section{Experiments on CityScapes}\label{sec:cityscapes_exp}
We also evaluate the performances of \algname{} on the CityScapes dataset \cite{cordts2016cityscapes}, which consists of 5000 street-scene images: 2975 for training, 500 for validation and 1525 for testing.
% recorded by car-mounted cameras with resolution 1024$\times$2048: 2975 images for training, 500 for validation and 1525 for testing. Objects with instance-level annotations belong to the following classes: person, rider, car, truck, bus, train, motorcycle, bicycle. 
See Appendix \ref{sec:appendix_cityscapes} for more details on how we fine-tuned the state-of-the-art proposal-free pipeline proposed in GMIS \cite{liu2018affinity} by using a \emph{S\o resen-Dice} loss, similarly to \cite{wolf2018mutex}.
%that achieved superior performances compared to other proposal-based methods like Mark R-CNN and employs a similar model to the one applied by us on neuron-segmentation.
% Their trained model was made publicly available, so we simply replaced their final graph-merging algorithm (MultiStepHAC) with \algname{}.  their instance branch model by using a \emph{S\o resen-Dice} loss similarly to \cite{wolf2018mutex} and obtained in this way sharper affinity-predictions.
Results are summarized in Table \ref{tab:results_cityscapes_val} and Fig. \ref{fig:cityscapes}: \algname{} with \emph{Average} linkage is the proposal-free method that achieves the best scores.
 Similarly to the previous experiments, other linkage criteria tend to over-cluster, like \emph{Abs Max}, or under-cluster and merge instances, like \emph{Sum}. The graph-merging algorithm proposed by \cite{liu2018affinity} (MultiStepHAC) requires the user to tune several threshold parameters and it was probably tailored to the original affinities predicted by them, so it did not generalize well to our fine-tuned model and it achieved lower scores compared to the original AP value of 34.1 reported in \cite{liu2018affinity}.  
Appendix - Table \ref{tab:extended_results_cityscapes_val} includes the scores of all other tested \algname{} algorithms.
\captionsetup[subtable]{labelformat=simple, labelsep=space, justification=centering, singlelinecheck=off}
\renewcommand*{\thesubtable}{(\alph{subtable})}
\begin{table}[t]
\centering
\begin{subtable}{0.5 \textwidth}
    \centering
    \scriptsize
        \begin{tabular}{l|l|cc}
%             & & \multicolumn{2}{c}{AP} \\
%            & Agglomeration  &  \multicolumn{2}{c}{Use constraints:} \\
%           Method & method & \textsc{No} & \textsc{Yes} \\ \midrule
% % DWT \cite{bai2017deep} & - & 21.2 & - \\
% SGN \cite{liu2017sgn} & - & 29.2 & - \\
% Mask R-CNN \cite{he2017mask} & - & 31.5 & - \\ \hline
%  & \textbf{\algname{} Average}& \textbf{34.3}  & 33.9  \\
% \multirow{2}{*}{GMIS Model \cite{liu2018affinity}} & MultiStepHAC \cite{liu2018affinity} & 33.0 & -  \\
%  % & \algname{} Max &   24.3  &   32.5  \\
%  & \algname{} Abs. Max. \cite{wolf2018mutex}  & 32.1 & 32.1 \\
%  & \algname{} Sum \cite{keuper2015efficient,levinkov2017comparative} & 31.3  & 31.9  \\

Method & Agglomeration type & AP \\ \midrule
% DWT \cite{bai2017deep} & - & 21.2 & - \\
% SGN \cite{liu2017sgn} & - & 29.2 & - \\
PANet \cite{liu2018path} & - & \textbf{36.5} \\
Mask R-CNN \cite{he2017mask} & - & 31.5 \\ \hline
 & \algname{} Average& 34.3 \\
 & \algname{} Average + Constraints & 33.9 \\
\multirow{2}{*}{GMIS Model \cite{liu2018affinity}} & MultiStepHAC \cite{liu2018affinity} & 33.0 \\
 % & \algname{} Max &   24.3  &   32.5  \\
 & \algname{} Abs. Max. \cite{wolf2018mutex}  & 32.1 \\
 & \algname{} Sum + Constraints  \cite{levinkov2017comparative} & 31.9  \\
 & \algname{} Sum \cite{keuper2015efficient} & 31.3 \\

 % & \algname{} Min &  0    & 0  \\
        \end{tabular}
    \caption{CityScapes \emph{validation} set}
    \label{tab:results_cityscapes_val}
\end{subtable}\hfill
\begin{subtable}{0.46\textwidth}
\centering
    \scriptsize
\begin{tabular}{l|cc}
           Method & AP  & AP 50\% \\ \midrule
           PANet \cite{liu2018path} & \textbf{31.8} & \textbf{57.1} \\
           \textbf{Ours: GMIS Model + \algname{} Average} & 28.3 & 47.0 \\ 
           GMIS \cite{liu2018affinity} & 27.3 & 45.6 \\
           Mask R-CNN \cite{he2017mask} & 26.2 & 49.9 \\
           SGN \cite{liu2017sgn} & 25.0 & 44.9 \\
           DIN \cite{arnab2017pixelwise} & 20.0 & 38.8 \\
           DWT \cite{bai2017deep} & 19.4 & 35.3 \\
           % SIAS\cite{} & 17.4 & 36.7 \\
           InstanceCut \cite{kirillov2017instancecut} & 13.0 & 27.9 \\

        \end{tabular}
    \caption{CityScapes \emph{test} set}
    \label{tab:results_cityscapes_test}
\end{subtable}
\caption{Average Precision scores (higher is better) on the CityScapes dataset. \algname{} with \emph{Average} linkage combined with the GMIS Model \cite{liu2018affinity} represents the proposal-free method achieving the best results (May 2019). We only compare methods that did not use external data (e.g. COCO \cite{lin2014microsoft}) for training.}
\end{table}

>>>>

% !TEX root = ../agglo_clust_review.tex
\section{Experiments on CityScapes}\label{sec:cityscapes_exp}
We also evaluate the performances of \algname{} on the CityScapes dataset \cite{cordts2016cityscapes}, which consists of 5000 street-scene images: 2975 for training, 500 for validation and 1525 for testing.
See Appendix \ref{sec:appendix_cityscapes} for more details on how we fine-tuned the state-of-the-art proposal-free pipeline proposed in GMIS \cite{liu2018affinity} by using a \emph{S\o resen-Dice} loss, similarly to \cite{wolf2018mutex}.
Results are summarized in Table \ref{tab:results_cityscapes_val} and Fig. \ref{fig:cityscapes}: \algname{} with \emph{Average} linkage achieves state-of-the-art results among proposal-free methods.
 Similarly to the previous experiments, other linkage criteria tend to over-cluster, like \emph{Abs Max}, or under-cluster and merge instances, like \emph{Sum}. The graph-merging algorithm proposed by \cite{liu2018affinity} (MultiStepHAC) requires the user to tune several threshold parameters and it was probably tailored to the original affinities predicted by them, so it did not generalize well to our fine-tuned model and it achieved lower scores compared to the original AP value of 34.1 reported in \cite{liu2018affinity}.  
Appendix - Table \ref{tab:extended_results_cityscapes_val} includes the scores of all other tested \algname{} algorithms.
\captionsetup[subtable]{labelformat=simple, labelsep=space, justification=centering, singlelinecheck=off}
\renewcommand*{\thesubtable}{(\alph{subtable})}
\begin{table}[t]
\centering
\begin{subtable}{0.5 \textwidth}
    \centering
    \scriptsize
        \begin{tabular}{l|l|cc}
            Method & Agglomeration type & AP \\ \midrule
            PANet \cite{liu2018path} & - & \textbf{36.5} \\
            Mask R-CNN \cite{he2017mask} & - & 31.5 \\ \hline
             & \algname{} Average& 34.3 \\
             & \algname{} Average + Constraints & 33.9 \\
            \multirow{2}{*}{GMIS Model \cite{liu2018affinity}} & MultiStepHAC \cite{liu2018affinity} & 33.0 \\
             & \algname{} Abs. Max. \cite{wolf2018mutex}  & 32.1 \\
             & \algname{} Sum + Constraints  \cite{levinkov2017comparative} & 31.9  \\
             & \algname{} Sum \cite{keuper2015efficient} & 31.3 \\
        \end{tabular}
    \caption{CityScapes \emph{validation} set}
    \label{tab:results_cityscapes_val}
\end{subtable}\hfill
\begin{subtable}{0.46\textwidth}
\centering
    \scriptsize
\begin{tabular}{l|cc}
           Method & AP  & AP 50\% \\ \midrule
           PANet \cite{liu2018path} & \textbf{31.8} & \textbf{57.1} \\
           \textbf{Ours: GMIS Model + \algname{} Average} & 28.3 & 47.0 \\ 
           GMIS \cite{liu2018affinity} & 27.3 & 45.6 \\
           Mask R-CNN \cite{he2017mask} & 26.2 & 49.9 \\
           SGN \cite{liu2017sgn} & 25.0 & 44.9 \\
           DIN \cite{arnab2017pixelwise} & 20.0 & 38.8 \\
           DWT \cite{bai2017deep} & 19.4 & 35.3 \\
           InstanceCut \cite{kirillov2017instancecut} & 13.0 & 27.9 \\
        \end{tabular}
    \caption{CityScapes \emph{test} set}
    \label{tab:results_cityscapes_test}
\end{subtable}
\caption{Average Precision scores (higher is better) on the CityScapes dataset. \algname{} with \emph{Average} linkage combined with the GMIS Model \cite{liu2018affinity} represents the proposal-free method achieving the best results (May 2019). We only compare methods that did not use external data (e.g. COCO \cite{lin2014microsoft}) for training.}
\end{table}

### 2019-06-25 chapters/5_experiments_intro.tex
Delete comments

We first evaluate and compare the agglomerative clustering algorithms described in the generalized framework on the task of neuron segmentation in electron microscopy (EM) image volumes. This application is of key interest in connectomics, a field of neuro-science with the goal of reconstructing neural wiring diagrams spanning complete central nervous systems. Currently, only proof-reading or manual tracing yields sufficient accuracy for correct circuit reconstruction \cite{schlegel2017learning}, thus further progress is required in automated reconstruction methods.
%First, we present how we predicted signed edge weights with a CNN. Then we introduce the CREMI challenge and our tested methods in Sec. \ref{sec:cremi_challenge} and finally we present our results in Sec. \ref{sec:results}.

% \subsection{Experimental setup: pixel grid-graph with long-range connections} \label{sec:grid_graph}
EM segmentation is commonly performed by first predicting 
% which pixels belong to a cell membrane using a CNN. As described in Sec. \ref{sec:related_work}, different postprocessing methods are then used to obtain a segmentation. The CNN can either be trained to predict 
boundary pixels \cite{beier2017multicut,ciresan2012deep} or undirected affinities \cite{wolf2018mutex,lee2017superhuman,funke2018large}, which represent how likely it is for a pair of pixels to belong to the same neuron segment. 
The affinities do not have to be limited to immediately adjacent pixels
Thus, similarly to \cite{lee2017superhuman}, we train a CNN to predict both short- and long-range affinities
and use them as edge weights of a 3D grid graph, where each node represents a pixel/voxel of the volume image. 
% In our experiments, we divided the set of edges $E$ in $E_{\mathrm{direct}}$ connecting direct neighboring voxels and $E_{\mathrm{long}}$. 
% See Appendix \ref{sec:training_details} for more details on the chosen neighborhood structure.
% , data augmentation and the training with L1 loss of the used 3D U-Net architecture \cite{ronneberger2015u,cciccek20163d}.
% We evaluate how beneficial long-range connections are by adding 
% The output layer of the CNN will then have $m_{\mathrm{direct}}+m_{\mathrm{long}}$ channels, where $m_{\mathrm{direct}}=6$ represents the direct neighbors in 3D and $m_{\mathrm{long}}$ is the number of long-range ones. 
% The output of the CNN can be represented as a weighted 3D grid graph, such that each node represents a pixel/voxel of the volume image. Each node is connected to its neighbors by $m_{\mathrm{direct}}$ edges ($E_{\mathrm{direct}}$) and $m_{\mathrm{long}}$ long-range ones ($E_{\mathrm{long}}$).
% In our experiments we evaluate how beneficial long-range connections are for the final segmentation and we add them to the graph with a given probability $p_{\mathrm{long}}$ (if $p_{\mathrm{long}}=0$, then $E_{\mathrm{long}}=\emptyset$).
% We note that the post-processing presented in \cite{lee2017superhuman} did not use any predicted long-range connection, whereas \cite{wolf2018mutex} introduced them with strides of 2 in the XY-plane.

>>>>

We first evaluate and compare the agglomerative clustering algorithms described in the generalized framework on the task of neuron segmentation in electron microscopy (EM) image volumes. This application is of key interest in connectomics, a field of neuro-science with the goal of reconstructing neural wiring diagrams spanning complete central nervous systems. Currently, only proof-reading or manual tracing yields sufficient accuracy for correct circuit reconstruction \cite{schlegel2017learning}, thus further progress is required in automated reconstruction methods.

EM segmentation is commonly performed by first predicting 
boundary pixels \cite{beier2017multicut,ciresan2012deep} or undirected affinities \cite{wolf2018mutex,lee2017superhuman,funke2018large}, which represent how likely it is for a pair of pixels to belong to the same neuron segment. 
The affinities do not have to be limited to immediately adjacent pixels
Thus, similarly to \cite{lee2017superhuman}, we train a CNN to predict both short- and long-range affinities
and use them as edge weights of a 3D grid graph, where each node represents a pixel/voxel of the volume image.

### 2019-06-25 chapters/5_experiments_noise.tex
Delete comments

\subsection{Results and discussion}\label{sec:results}
% \subsection{In-depth comparison of different linkage criteria for \algname{}} 
\textbf{Comparison of linkage criteria} Table \ref{tab:results_cremi_train} shows how the agglomerative algorithms derived from our framework compare to each other. For a simple baseline, we also include a segmentation produced by thresholding the affinity predictions (THRESH).
% The poor scores achieved by THRESH highlight the difficulty of the task. 
\algname{} with \emph{Average} linkage, representing one of the new algorithms derived from our generalized framework, significantly outperformed all other previously proposed agglomerative methods like GAEC (\algname{} Sum) \cite{keuper2015efficient}, Greedy Fixation (\algname{} Sum + Constraints) \cite{levinkov2017comparative} or Mutex Watershed (\algname{} Abs. Max.) \cite{wolf2018mutex}. The competitive performance of this simple parameter-free algorithm is also reported in Table \ref{tab:results_cremi_test}, showing the current leader-board of the challenge: all entries, apart from \algname{}, employ superpixel-based post-processing pipelines, several of which rely on the lifted multicut formulation of \cite{beier2017multicut} that uses several random forests to predict graph edge weights, relying not only on information derived from affinity maps but also raw data and shape information.
Note that the test volumes contain several imaging artifacts that make segmentation particularly challenging and might profit from more robust edge statistics of super-pixel based approaches.
On the other hand, the fact that our algorithm can operate on pixels directly removes the parameter tuning necessary to obtain good super-pixels and can also avoid errors that result from wrong superpixels that cannot be fixed during later agglomeration.
In Appendix \ref{sec:appendix_exps_full_cremi}, we provide more details about how we scaled up \algname{} to the full datasets. Appendix Table \ref{tab:extended_results_cremi} lists the performances and the run-times for all tested \algname{} linkage.

\begin{figure}[t]
        \centering
\begin{minipage}[t]{0.56\textwidth}
% \begin{table}
    \centering
    \scriptsize
    % \begin{subtable}[t!]{0.5\textwidth}\centering
        \begin{tabular}[t]{l|c}
        % \toprule
        % & \multicolumn{2}{c}{\thead{Add Cannot-Link Constraints:}} \\
         % & \multicolumn{1}{c}{\thead{\textsc{No}}} & \multicolumn{1}{c}{\thead{\textsc{Yes}}} \\ \midrule
          & \makecell{CREMI-Score \\(lower is better)} \\ \midrule 
         % & \multicolumn{1}{c}{\thead{$\beta$}}  & \thead{AP} & \multicolumn{1}{c}{\thead{$\beta$}} & \thead{AP} \\ \midrule\midrule
\textbf{\algname{}} \textbf{Average}& \textbf{0.226}  \\
\algname{} Sum + Constraints \cite{levinkov2017comparative} & 0.282 \\
% Our UNet + DTWS + MC & -& 0.310 \\
% Our UNet + DTWS + LMC & -& 0.317 \\
\algname{} Abs. Max. \cite{wolf2018mutex} & 0.322 \\
\algname{} Max. + Constraints & 0.324 \\
\algname{} Sum \cite{keuper2015efficient} & 0.334 \\
\algname{} Average + Constraints & 0.563 \\
THRESH & 1.521 \\ 
% \textbf{\algname{}} & \textbf{Average}& \textbf{0.936 $\pm$ 0.004}  \\
% Greedy Fixation \cite{levinkov2017comparative} & Sum + Constr. & 0.906 $\pm$ 0.022 \\
% DTWS + LMC & -& 0.903 $\pm$ 0.016 \\
% DTWS + MC & -& 0.903 $\pm$ 0.017 \\
% % DTWS + avgHC &-& \\
% % DTWS + MC (SR)& -& 0.900 $\pm$ 0.019 \\
% % DTWS + LMC (SR)& -& 0.898 $\pm$ 0.017 \\
% Mutex Watershed \cite{wolf2018mutex} & Abs. Max.  & 0.897 $\pm$ 0.012 \\
% GAEC \cite{keuper2015efficient} & Sum & 0.872 $\pm$ 0.028 \\
% THRESH &-& 0.221  $\pm$ 0.067 \\ 
% % DTWS + \algname{} & Average& \TODO{} \\
% % DTWS  & -& 0.010 $\pm$ 0.003\\
        \end{tabular}
    \captionof{table}{CREMI-Scores achieved by different linkage criteria and thresholding. All methods use the affinity predictions from our CNN as input. Scores are averages over the three CREMI training datasets.}
    \label{tab:results_cremi_train}
\end{minipage}\hfill
\begin{minipage}[t]{0.4\textwidth}
    \centering
    \scriptsize
        \begin{tabular}[t]{l|c}
         & \makecell{CREMI-Score \\(lower is better)}  \\ \midrule
Our CNN + DTWS + LMC &  0.221\\
PNI CNN \cite{lee2017superhuman} & 0.228 \\
\textbf{Our CNN + \algname{} Average} & \textbf{0.241} \\
MALA CNN + MC \cite{funke2018large} & 0.276 \\
CRU-Net \cite{zeng2017deepem3d} & 0.566  \\
LFC \cite{parag2017anisotropic} & 0.616  \\
% Our UNet + DTWS + LMC &  \textbf{0.221} & \textbf{0.108}\\
% PNI-UNet & 0.228 & 0.116 \\
% Our UNet + \algname{} Avg-Linkage & 0.244 & 0.130 \\
% MALA-UNet + MC \cite{funke2018large} & 0.276 & 0.132 \\
% CRUNet \cite{zeng2017deepem3d} & 0.566 & 0.229 \\
% LFC \cite{parag2017anisotropic} & 0.616 & \\
        \end{tabular}
        \vspace*{1em}
    \captionof{table}{Current leading entries  in the CREMI challenge leaderboard \cite{cremiChallenge} (May 2019). The scores are averages of the three test datasets.}
    \label{tab:results_cremi_test}
\end{minipage}
\end{figure}
\captionsetup[subfigure]{justification=centering, singlelinecheck=off}
\begin{figure}
\centering
    %     \begin{subfigure}[t]{0.49 \textwidth}
    %     \centering
    %     \includegraphics[width=\textwidth,trim=0.55in 0.35in 0.65in 0.80in,clip]{./figs/merge_noise_only_direct.pdf}

    %     \caption{Without long-range edges: $p_{\mathrm{long}}=0$} \label{fig:merge_noise_only_direct}
    % \end{subfigure} \hfill
    % \begin{subfigure}[t]{0.49 \textwidth}
    %     \centering
    %     \includegraphics[width=\textwidth,trim=0.53in 0.35in 0.65in 0.80in,clip]{./figs/merge_noise_long_range.pdf}
    %     \caption{With long-range edges: $p_{\mathrm{long}}=0.1$} \label{fig:merge_noise_with_long_range}
    % \end{subfigure}
    \begin{subfigure}[t]{0.49 \textwidth}
        \centering
        \includegraphics[width=\textwidth,trim=0.55in 0.1in 0.65in 0.45in,clip]{./figs/noise_plots/under_segment_plots_0.pdf}
        % \caption{Without long-range edges: $p_{\mathrm{long}}=0$} \label{fig:merge_noise_only_direct}
    \end{subfigure} \hfill
    \begin{subfigure}[t]{0.49 \textwidth}
        \centering
        \includegraphics[width=\textwidth,trim=0.53in 0.1in 0.65in 0.45in,clip]{./figs/noise_plots/under_segment_plots_1.pdf}
        % \caption{With long-range edges: $p_{\mathrm{long}}=0.1$} \label{fig:merge_noise_with_long_range}
    \end{subfigure}

        \begin{subfigure}[t]{0.49 \textwidth}
        \centering
        \includegraphics[width=\textwidth,trim=0.53in 0.1in 0.65in 0.45in,clip]{./figs/noise_plots/over_segment_plots_0.pdf}
        \caption{No long-range predictions: $p_{\mathrm{long}}=0$} \label{fig:merge_noise_only_direct}
    \end{subfigure} \hfill
    \begin{subfigure}[t]{0.49 \textwidth}
        \centering
        \includegraphics[width=\textwidth,trim=0.53in 0.1in 0.65in 0.45in,clip]{./figs/noise_plots/over_segment_plots_1.pdf}
        \caption{With long-range predictions: $p_{\mathrm{long}}=0.1$} \label{fig:merge_noise_with_long_range}
    \end{subfigure}
\caption{\algname{} sensitivity to noise: \emph{Average} linkage proved to be the most robust. Performances are given by Rand-Score (higher is better) depending on the amount of noise added to the CNN predictions. Solid lines represent median values over 30 experiments. Values between the 25th and the 75th percentile are shown in shaded areas. The two sets of experiments using under- and over-clustering noise are summarized in the plots at the top and at the bottom, respectively (see Appendix \ref{sec:appendix_noise_gen} for more details). For each experiment, some of the long-range CNN predictions were randomly selected with probability $p_{\mathrm{long}}$ and added as long-range edges to the pixel grid-graph.
%\textbf{Bottom}: Multicut objective (Eq. \ref{eq:multicut_obj}), measuring how balanced the final clusterings are (lower is better); for a clearer comparison, an offset is added to the energy values, so that the method achieving the lowest energy is always assigned to value zero. 
}\label{fig:noise_plots}
\end{figure}
% \begin{minipage}[b]{0.48\textwidth}
% % \begin{figure}
%         % \begin{subfigure}[t]{0.48 \textwidth}
%         \centering
%         \includegraphics[width=0.98\textwidth,trim=0.35in 0.35in 0.35in 0.35in,clip]{./figs/merge_noise.pdf}
%         \captionof{subfigure}{Merge-biased opensimplex noise} \label{fig:thresh}
%     \end{minipage}\hfil
% \begin{minipage}[b]{0.48\textwidth}
%     % \end{subfigure}%
%     % \begin{subfigure}[t]{0.48 \textwidth}
%         \centering
%         \includegraphics[width=0.98\textwidth,trim=0.29in 0.31in 0.31in 0.31in,clip]{./figs/split_noise.pdf}
%         \captionof{subfigure}{Split-biased opensimplex noise} \label{fig:ws}
%     % \end{subfigure}
% \captionof{figure}{Plot illustrating Adapted RAND scores achieved by UGACA and different update rules when noise is added to the edge weights... Solid lines represent median values, whereas values between the 25th and the 75th percentile are shown in shade areas.    \TODO{Label which uses only local-neighbors and which uses long-range connections}}\label{fig:noise_plots}
% % \end{figure}

\textbf{Noise experiments }  Additionally, we conduct a set of experiments where the CNN predictions are perturbed by structured noise, in order to highlight the properties of each \algname{} variant and perform an in-depth comparison that is as quantitative as possible. Appendix \ref{sec:appendix_noise_gen} introduces the type of spatially correlated noise that allowed us to perturb the CNN outputs by introducing simulated additional artifacts like missing or false positive boundary evidence. 
Fig. \ref{fig:noise_plots} summarizes our 12000 noise experiments: we focus on the best performing linkage criteria, i.e. \emph{Average}, \emph{Sum} and \emph{Abs Max}, and test them with different amount of noise. 
In these experiments, we also want to assess how beneficial it is to use long-range CNN predictions in the agglomeration. Thus, we perform a set of simulations without adding long-range connections to the grid-graph and another set where we introduce them with a 10\% probability\footnote{We also performed experiments adding all the long-range predictions given by the CNN model, but we did not note major differences when using only 10\% of them. Adding this fraction is usually sufficient to improve the scores.}.
%, both with and without use of long-range connections in the grid-graph. % In Fig. \ref{fig:noise_plots}, we used a merge-biased noise decreasing boundary evidence. See Fig. \ref{fig:noise_split} in Appendix for a split-biased version.

@@

\textbf{Sum linkage } 
% The \emph{Sum} linkage generally outputs the most balanced graph partitioning according to the objective defined in Eq. \ref{eq:multicut_obj} and is then confirmed to be a good choice for initializing more complex approximations of the multicut optimization problem like \cite{beier2016efficient}. 
All our experiments show that \algname{} with \emph{Sum} linkage is the algorithm with the highest tendency to under-cluster and incorrectly merge segments (see Fig. \ref{fig:cremi_comparison} for an example). This property is related to the empirical observation that a \emph{Sum} statistic tends to grow clusters one after the other, as shown in Fig. \ref{fig:intro_figure} by the quite unique agglomeration order of the \emph{Sum} statistic. An intuitive explanation of this fact is the following: initially, most of the intra-cluster nodes present similar attractive interactions between each others; when the two nodes sharing the most attractive interaction are merged, there is a high chance that they both share an attractive interaction with a common neighboring node, so the new interaction with this common neighbor will be immediately assigned to a high priority in the agglomeration, given by the sum of two high weights; this usually starts a ``chain reaction'', where only a single cluster is agglomerated at the beginning. On the other hand, as we also see in Fig. \ref{fig:intro_figure}, other linkage criteria like \emph{Average} or \emph{Abs Max} grow clusters of similar sizes in parallel and accumulate in this way much more reliable inter-cluster statistics.

>>>>

\subsection{Results and discussion}\label{sec:results}
\textbf{Comparison of linkage criteria} Table \ref{tab:results_cremi_train} shows how the agglomerative algorithms derived from our framework compare to each other. For a simple baseline, we also include a segmentation produced by thresholding the affinity predictions (THRESH).
\algname{} with \emph{Average} linkage, representing one of the new algorithms derived from our generalized framework, significantly outperformed all other previously proposed agglomerative methods like GAEC (\algname{} Sum) \cite{keuper2015efficient}, Greedy Fixation (\algname{} Sum + Constraints) \cite{levinkov2017comparative} or Mutex Watershed (\algname{} Abs. Max.) \cite{wolf2018mutex}. The competitive performance of this simple parameter-free algorithm is also reported in Table \ref{tab:results_cremi_test}, showing the current leader-board of the challenge: all entries, apart from \algname{}, employ superpixel-based post-processing pipelines, several of which rely on the lifted multicut formulation of \cite{beier2017multicut} that uses several random forests to predict graph edge weights, relying not only on information derived from affinity maps but also raw data and shape information.
Note that the test volumes contain several imaging artifacts that make segmentation particularly challenging and might profit from more robust edge statistics of super-pixel based approaches.
On the other hand, the fact that our algorithm can operate on pixels directly removes the parameter tuning necessary to obtain good super-pixels and can also avoid errors that result from wrong superpixels that cannot be fixed during later agglomeration.
In Appendix \ref{sec:appendix_exps_full_cremi}, we provide more details about how we scaled up \algname{} to the full datasets. Appendix Table \ref{tab:extended_results_cremi} lists the performances and the run-times for all tested \algname{} linkage.

\begin{figure}[t]
        \centering
\begin{minipage}[t]{0.56\textwidth}
    \centering
    \scriptsize
        \begin{tabular}[t]{l|c}
          & \makecell{CREMI-Score \\(lower is better)} \\ \midrule 
\textbf{\algname{}} \textbf{Average}& \textbf{0.226}  \\
\algname{} Sum + Constraints \cite{levinkov2017comparative} & 0.282 \\
\algname{} Abs. Max. \cite{wolf2018mutex} & 0.322 \\
\algname{} Max. + Constraints & 0.324 \\
\algname{} Sum \cite{keuper2015efficient} & 0.334 \\
\algname{} Average + Constraints & 0.563 \\
THRESH & 1.521 \\ 
        \end{tabular}
    \captionof{table}{CREMI-Scores achieved by different linkage criteria and thresholding. All methods use the affinity predictions from our CNN as input. Scores are averages over the three CREMI training datasets.}
    \label{tab:results_cremi_train}
\end{minipage}\hfill
\begin{minipage}[t]{0.4\textwidth}
    \centering
    \scriptsize
        \begin{tabular}[t]{l|c}
         & \makecell{CREMI-Score \\(lower is better)}  \\ \midrule
Our CNN + DTWS + LMC &  0.221\\
PNI CNN \cite{lee2017superhuman} & 0.228 \\
\textbf{Our CNN + \algname{} Average} & \textbf{0.241} \\
MALA CNN + MC \cite{funke2018large} & 0.276 \\
CRU-Net \cite{zeng2017deepem3d} & 0.566  \\
LFC \cite{parag2017anisotropic} & 0.616  \\
        \end{tabular}
        \vspace*{1em}
    \captionof{table}{Current leading entries  in the CREMI challenge leaderboard \cite{cremiChallenge} (May 2019). The scores are averages of the three test datasets.}
    \label{tab:results_cremi_test}
\end{minipage}
\end{figure}
\captionsetup[subfigure]{justification=centering, singlelinecheck=off}
\begin{figure}
\centering
    \begin{subfigure}[t]{0.49 \textwidth}
        \centering
        \includegraphics[width=\textwidth,trim=0.55in 0.1in 0.65in 0.45in,clip]{./figs/noise_plots/under_segment_plots_0.pdf}
    \end{subfigure} \hfill
    \begin{subfigure}[t]{0.49 \textwidth}
        \centering
        \includegraphics[width=\textwidth,trim=0.53in 0.1in 0.65in 0.45in,clip]{./figs/noise_plots/under_segment_plots_1.pdf}
    \end{subfigure}

        \begin{subfigure}[t]{0.49 \textwidth}
        \centering
        \includegraphics[width=\textwidth,trim=0.53in 0.1in 0.65in 0.45in,clip]{./figs/noise_plots/over_segment_plots_0.pdf}
        \caption{No long-range predictions: $p_{\mathrm{long}}=0$} \label{fig:merge_noise_only_direct}
    \end{subfigure} \hfill
    \begin{subfigure}[t]{0.49 \textwidth}
        \centering
        \includegraphics[width=\textwidth,trim=0.53in 0.1in 0.65in 0.45in,clip]{./figs/noise_plots/over_segment_plots_1.pdf}
        \caption{With long-range predictions: $p_{\mathrm{long}}=0.1$} \label{fig:merge_noise_with_long_range}
    \end{subfigure}
\caption{\algname{} sensitivity to noise: \emph{Average} linkage proved to be the most robust. Performances are given by Rand-Score (higher is better) depending on the amount of noise added to the CNN predictions. Solid lines represent median values over 30 experiments. Values between the 25th and the 75th percentile are shown in shaded areas. The two sets of experiments using under- and over-clustering noise are summarized in the plots at the top and at the bottom, respectively (see Appendix \ref{sec:appendix_noise_gen} for more details). For each experiment, some of the long-range CNN predictions were randomly selected with probability $p_{\mathrm{long}}$ and added as long-range edges to the pixel grid-graph.
}\label{fig:noise_plots}
\end{figure}

\textbf{Noise experiments }  Additionally, we conduct a set of experiments where the CNN predictions are perturbed by structured noise, in order to highlight the properties of each \algname{} variant and perform an in-depth comparison that is as quantitative as possible. Appendix \ref{sec:appendix_noise_gen} introduces the type of spatially correlated noise that allowed us to perturb the CNN outputs by introducing simulated additional artifacts like missing or false positive boundary evidence. 
Fig. \ref{fig:noise_plots} summarizes our 12000 noise experiments: we focus on the best performing linkage criteria, i.e. \emph{Average}, \emph{Sum} and \emph{Abs Max}, and test them with different amount of noise. 
In these experiments, we also want to assess how beneficial it is to use long-range CNN predictions in the agglomeration. Thus, we perform a set of simulations without adding long-range connections to the grid-graph and another set where we introduce them with a 10\% probability\footnote{We also performed experiments adding all the long-range predictions given by the CNN model, but we did not note major differences when using only 10\% of them. Adding this fraction is usually sufficient to improve the scores.}.

@@

\textbf{Sum linkage } 
All our experiments show that \algname{} with \emph{Sum} linkage is the algorithm with the highest tendency to under-cluster and incorrectly merge segments (see Fig. \ref{fig:cremi_comparison} for an example). This property is related to the empirical observation that a \emph{Sum} statistic tends to grow clusters one after the other, as shown in Fig. \ref{fig:intro_figure} by the quite unique agglomeration order of the \emph{Sum} statistic. An intuitive explanation of this fact is the following: initially, most of the intra-cluster nodes present similar attractive interactions between each others; when the two nodes sharing the most attractive interaction are merged, there is a high chance that they both share an attractive interaction with a common neighboring node, so the new interaction with this common neighbor will be immediately assigned to a high priority in the agglomeration, given by the sum of two high weights; this usually starts a ``chain reaction'', where only a single cluster is agglomerated at the beginning. On the other hand, as we also see in Fig. \ref{fig:intro_figure}, other linkage criteria like \emph{Average} or \emph{Abs Max} grow clusters of similar sizes in parallel and accumulate in this way much more reliable inter-cluster statistics.
